The regularity of ODEs and thimble integrals \\ with respect to Borel summation \begin{draft}\textbf{[DRAFT]}\end{draft}

### 2024-06-02 exp-resurgence.tex
Go over new calculation of Laplace transform of convolution

%%\textcolor{orange}{[Where does resurgence come in?]}
\subsubsection{Solving Riemann--Hilbert problems}
Sometimes level 1 ODEs can be regarded as the local version of some global operators, namely as meromorphic connections on some principal bundles (also known as \textit{opers}~\cite{BD-opers}). In this case, solutions of the ODE are (local) flat sections for the corresponding connection. Therefore, we could use the theory of meromorphic connections to study ODEs, in particular by solving a Riemann--Hilbert problem.

@@

The Laplace transform $\laplace^\theta_{\zeta,\alpha}$ is a homomorphism from the algebra of locally integrable, exponentially bounded holomorphic functions, equipped with the convolution product, to the algebra of analytic functions on the half-plane $\Re(e^{i\theta} z) > 0$, equipped with the usual product.

@@

   \textbf{V} temptative proof

@@

        &=\int_{\Gamma_{\zeta'',0}}d\zeta'' \,e^{-z\zeta''}  \psi'' \,\int_{\Gamma_{t,0}} dt\, e^{-zt} \phi\\
   where we have introduced the coordinate $t=\zeta''\frac{s}{1-s}+\alpha$ which gives the ray $\Gamma_{t,0}$ as $s$ varies in $[0,1]$.

>>>>

%%\textcolor{orange}{[Where does resurgence come in?]}
\subsubsection{Solving Riemann--Hilbert problems}
\begin{todo}[\textbf{A} Read through]\end{todo} Sometimes level 1 ODEs can be regarded as the local version of some global operators, namely as meromorphic connections on some principal bundles (also known as \textit{opers}~\cite{BD-opers}). In this case, solutions of the ODE are (local) flat sections for the corresponding connection. Therefore, we could use the theory of meromorphic connections to study ODEs, in particular by solving a Riemann--Hilbert problem.

@@

\begin{todo}[Correct and rewrite!]\end{todo}
\begin{old}The Laplace transform $\laplace^\theta_{\zeta,\alpha}$ is a homomorphism from the algebra of locally integrable, exponentially bounded holomorphic functions, equipped with the convolution product, to the algebra of analytic functions on the half-plane $\Re(e^{i\theta} z) > 0$, equipped with the usual product.\end{old}
\begin{todo}[Check: if Laplace transform of convolution is well-defined, then product of Laplace transforms is well-defined]\end{todo}
\begin{todo}[\textbf{A} \textbf{V} Redo argument with $\ast_{\zeta, \beta}$]\end{todo}
\laplace_{\zeta,\alpha}[{\phi}\ast_{\zeta,\alpha}{\psi}] & = \laplace_{\zeta,\alpha}[{\phi}]\,\laplace_{\zeta,0}[{\psi}]

@@

   \textbf{V} fix notation, add $\theta$

@@

        &=\int_{\Gamma_{\zeta'',0}}d\zeta'' \,e^{-z\zeta''}  \psi'' \,\int_{\Gamma_{t,\alpha}} dt\, e^{-zt} \phi\\
   where we have introduced the coordinate $t=\zeta''\frac{s}{1-s}+\alpha$ which gives the ray $\Gamma_{t,\alpha}$ as $s$ varies in $[0,1]$. \begin{todo}[Check claim: as coordinates on the position domain, $t = \zeta'$. If true, clarify argument.]\end{todo}
